Joshua 2.0: A Toolkit for Parsing-Based Machine Translation \\with Syntax, Semirings, Discriminative Training and Other Goodies

### 2010-06-03 papers/wmt10/joshua-progress.tex
Fixed typos mentioned by reviewer 2, added citations for R-PROP and L-BFGS.
git-svn-id: https://joshua.svn.sourceforge.net/svnroot/joshua/branches/publications@1699 0ae5e6b2-d358-4f09-a895-f82f13dd62a4

\joshua is an open-source toolkit for parsing-based machine translation that is
written in Java. The initial release of \joshua  \cite{joshua-wmt09} was
a re-implementation of the Hiero system \cite{hiero-2007} and all its
associated algorithms, including: chart parsing, $n$-gram language model
integration, beam and cube pruning, and $k$-best extraction.  The \joshua 1.0
release also included re-implementations of suffix array grammar extraction
\cite{lopez:2007:EMNLP-CoNLL2007,PBML-2010-Joshua-grammar-extraction} and
minimum error rate training \cite{och-mert,Zaidan2009}.  Additionally, it
included parallel and distributed computing techniques for salability \cite{Joshua-old}.

@@

The initial release of \joshua supported only Hiero-style SCFGs, which use a single nonterminal symbol X.  This release includes support for arbitrary SCFGs, including ones that use a rich set of linguistic nonterminal symbols.  
In particular we have added support for \newcite{samt2006}'s syntax-augmented machine
translation. SAMT grammar extraction is identical to Hiero grammar extraction, except that one side of the parallel is parsed, and syntactic labels replace the X
nonterminals in Hiero-style rules.  Instead of extracting this Hiero rule from the bitext

@@

Discriminative training with a large number of features has 
potential to improve the MT performance.
We have implemented the hypergraph-based minimum risk training \cite{li-eisner:2009:EMNLP},
which minimizes the {\em expected loss} of the reference translations.
The minimum-risk objective can be optimized by a gradient-based method, where
the risk and its gradient can be computed using a second-order expectation semiring.
For optimization, we use both L-BFGS\footnote{http://en.wikipedia.org/wiki/L-BFGS} 
and Rprop\footnote{http://en.wikipedia.org/wiki/Rprop}.

>>>>

\joshua is an open-source toolkit for parsing-based machine
translation that is written in Java. The initial release of \joshua
\cite{joshua-wmt09} was a re-implementation of the Hiero system
\cite{hiero-2007} and all its associated algorithms, including: chart
parsing, $n$-gram language model integration, beam and cube pruning,
and $k$-best extraction.  The \joshua 1.0 release also included
re-implementations of suffix array grammar extraction
\cite{lopez:2007:EMNLP-CoNLL2007,PBML-2010-Joshua-grammar-extraction}
and minimum error rate training \cite{och-mert,Zaidan2009}.
Additionally, it included parallel and distributed computing
techniques for scalability \cite{Joshua-old}.

@@

The initial release of \joshua supported only Hiero-style SCFGs, which
use a single nonterminal symbol X.  This release includes support for
arbitrary SCFGs, including ones that use a rich set of linguistic
nonterminal symbols.  In particular we have added support for
\newcite{samt2006}'s syntax-augmented machine translation. SAMT
grammar extraction is identical to Hiero grammar extraction, except
that one side of the parallel corpus is parsed, and syntactic labels
replace the X nonterminals in Hiero-style rules.  Instead of
extracting this Hiero rule from the bitext

@@

Discriminative training with a large number of features has potential
to improve the MT performance.  We have implemented the
hypergraph-based minimum risk training \cite{li-eisner:2009:EMNLP},
which minimizes the {\em expected loss} of the reference translations.
The minimum-risk objective can be optimized by a gradient-based
method, where the risk and its gradient can be computed using a
second-order expectation semiring.  For optimization, we use both
L-BFGS \cite{lbfgs} and Rprop \cite{rprop}.
